Should I Fuzz my Inputs or Improve my Test Suite? Lessons from Differential Testing Runtime Engines.

### 2018-06-13 paper/paper.tex
pass on intro

\title{Finding Functional Bugs in JavaScript Engines with Differential
  Testing---an Experience Report}

@@

\begin{abstract}
\end{abstract}

@@

JavaScript (\js{}) is one of the most popular programming languages of
today~\cite{business-insider,stackify}. The \js{} specification
changes relatively frequently to accommodate the pressing demands of
the community. For example, the JS specification went through a severe
change recently called by the name of ECMAScript6
(ES6)~\cite{es6-features}.  These changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated techniques can help finding
bugs, but the lack of executable specifications limits their ability
to detect errors not manifested by universal oracles.

This paper reports on a study to find those kinds of bugs in
JavaScript engines. The goal of the study is to improve quality of
existing \js{} engines by improving the bug-finding process. We used
differential testing~\cite{Brumley-etal-ss07}, a technique that has
been applied in a variety of
contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to address the oracle problem. Differential testing leverages the
diversity across system's implementations to detect anomalous
behavior. \Mar{this needs work$\rightarrow$}
\Fix{but it has not been thoroughly explored to find functional bugs in JS
engines. The closest work was done by Patra and
Pradel~\cite{patra2016learning}, where they evaluated their proposed
language-agnostic fuzzer to find cross-browser HTML+JS
discrepancies. This project aims at building and evaluating an
infrastructure for differential testing of runtime engines, such as
the JS engine or WebAssembly's. The sensible parts of the
infrastructure are the checks of input validity (as to reduce
waste/cost) and output correctness (as to reduce false positives).}

@@

\begin{table*}[ht!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

\Fix{talk about students...}

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing, we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing, we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing, we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

The independent variable of our experiment is the fuzzing strategy as
represented by various fuzzing tools. Our dependent variables are (i)
the ratio of bugs found with fuzzing as opposed to no fuzzing and (ii)
and the ratio of bugs found for each fuzzing strategy. We consider a
search successful only if it lends in a bug confirmed by the
developers of the affected engine. In short, our experiment assesses
the impact of these factors in bug-finding ability.

Considering the ratio of bugs found with fuzzing versus no fuzzing, we
want to observe how often fuzzing really helps. In the limit, all bugs
could be found without extra inputs, \ie{}, simply executing the seed
inputs on each engine and comparing their outcomes. Recall that we
mined test suites from a variety of sources. Considering the fuzzing
strategy, it is important to understand whether a fuzzing strategy is
particularly prominent.

@@

@@

>>>>

\title{Should I Fuzz my Inputs or Improve my Test Suite? Lessons from
  Differential Testing Runtime Engines.}

@@

\begin{abstract}
Differential testing has shown to be a successful approach to finding
bugs in compilers and runtime engines. This paper assesses the impact
that the fuzzing strategy and the test suites have in bug-finging
ability. We focused on JavaScript and WebAssembly runtime
engines. \Fix{...}
\end{abstract}

@@

JavaScript (\js{}) is one of the most popular programming languages
for the web today~\cite{business-insider,stackify}. The interest of
the community in the JS ecossystem incentivizes improvements both in
the language and their runtime engine implementations. It is natural
to expect that such improvements will entail sensible changes in
engine implementations~\cite{kangax} that could lead to
errors. Finding bugs on JS engines is therefore and important
problem. Automated techniques, such as Fuzz Testing~\cite{fuzz-bart},
have shown successful at finding universal errors, such as memory
errors~\cite{libfuzzer-tutorial}. However, they don't address the
problem of finding functional errors that could arise when an engine
does not adhere to the specification.

This paper reports on a study to find those kinds of bugs in
JavaScript engines.\Mar{revise...a study answer questions? the
  statement is more propositive.} The goal of the study is to improve
quality of existing \js{} engines by improving the bug-finding
process. We used differential testing~\cite{Brumley-etal-ss07}, a
technique that has been applied in a variety of
contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to address the oracle problem. Differential testing leverages the
diversity across system's implementations to detect anomalous
behavior. \Mar{this needs work$\rightarrow$} \Fix{but it has not been
  thoroughly explored to find functional bugs in JS engines. The
  closest work was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

The goal of this study is to assess the impact of fuzzing in finding
bugs with differential testing.

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

The independent variable of our experiment is the fuzzing strategy as
implemented by various fuzzing tools. Our dependent variables are (i)
the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
the ratio of bugs found with each fuzzing strategy. We consider a
search successful only if it lends in a bug confirmed by the
developers of the affected engine.  The rationale for considering the
ratio of bugs found with fuzzing versus no fuzzing is to observe how
often fuzzing really helps in this scenario. In the limit, all bugs
could be found without extra inputs, \ie{}, simply executing the seed
inputs on each engine and comparing their outcomes. Recall that we
mined test suites from a variety of sources. The rationale for
considering the fuzzing strategy is to understand to which extent each
strategy--as implemented by representative tools--helps in this
context.

@@

\Mar{justify why we discuss these bugs} \Mar{discuss other bugs}

@@

\section{Results}

\subsection{Fuzzing versus No Fuzzing}

\subsection{Fuzzing Strategy}

\section{Related Work}

RFC-Directed Differential Testing of Certificate Validation in SSL/TLS Implementations...[ICSE18]
